Contracts for Contracts

### 2023-06-14 paper/introduction.tex
some bits of intro

%Apart from the investigating effort to certify and verify smart contract
%programs, language designers are responsible to empower programmers with better
%linguistic solutions to secure smart contracts in the first place.
To address these issues, we argue that \emph{behavioral software
contracts}~\cite{DBLP:conf/tools/Meyer98a} should play a fundamental role in
the development of \emph{smart contract} programs.
Similar to smart contracts, behavioral contracts is an agreement, too. They
specify assumptions and guarantees between software components, just as
smart contracts specify assumptions and guarantees between economic parties.
In languages with behavioral contracts, the specified assumptions and
guarantees will be monitored and reported when violated.

Pioneered by the Eiffel language \cite{DBLP:books/ph/Meyer91} and the
design-by-contract methodology \cite{DBLP:conf/tools/Meyer98a}, various styles
of behavioral contracts have been adopted in Java, Haskell, C\#, Python,
Racket, Elixir \cite{DBLP:conf/erlang/0001BBHMEF22}, etc. \note{cite}
In this paper, we develop a behavioral contract system \lang (Contract
Solidity) for the Solidity language, providing a practical specification and
monitoring system for both \emph{higher-order and temporal behaviors}.
Solidity is a programming language to build smart contract programs that run on
the Ethereum platform.  As one of the most popular ecosystem of smart
contracts, Solidity has been used \todo{to do cool things}.
\todo{explain challenges}

>>>>

%Apart from the investigating effort to certify and verify smart contract
%programs, language designers are responsible to empower programmers with better
%linguistic solutions to secure smart contracts in the first place.
To address these issues, we argue that \emph{behavioral software
contracts}~\cite{DBLP:conf/tools/Meyer98a} should play a fundamental role in
the development of \emph{smart contract} programs.
Similar to smart contracts, behavioral contracts is an agreement, too. They
specify assumptions and guarantees between software components, just as
smart contracts specify assumptions and guarantees between economic parties.
The specified assumptions and guarantees are executable specifications
using the same programming language syntax, and will be monitored and reported
if violated.
Pioneered by the Eiffel language \cite{DBLP:books/ph/Meyer91} and the
design-by-contract methodology \cite{DBLP:conf/tools/Meyer98a,
DBLP:books/ph/Meyer97}, various styles of behavioral contracts have been
adopted in Java, Haskell, C\#, Python, Racket, Elixir
\cite{DBLP:conf/erlang/0001BBHMEF22}, etc. \note{cite}
Studies \cite{DBLP:conf/rodin/Chalin06, DBLP:books/ph/Meyer97}
have shown that behavioral contracts can support design, development,
testing, and debugging of software systems.

In this paper, we develop a behavioral contract system \lang (Contract
Solidity) for the Solidity language, providing a practical specification and
monitoring system for both \emph{higher-order and temporal behaviors}.
Solidity is a programming language to build smart contract programs that run on
the Ethereum platform.  As one of the most popular ecosystem of smart
contracts, Solidity has been used \todo{to do cool things}.
\todo{explain challenges}
